---
title: "Econ 2814 Assignment 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


PARID
PROPERTYHOUSENUM.x
PROPERTYADDRESS
PROPERTYZIP.x
SCHOOLCODE.x
SALEDATE.x
SALEPRICE
SALECODE.x
STORIES
YEARBLT
CONDITION
TOTALROOMS
BEDROOMS
FULLBATHS
HALFBATHS
HEATINGCOOLING
CONDITION
BSMTGARAGE
FINISHEDLIVINGAREA

```{r}
library(tidyverse)
library(lubridate)
library(lemon)
```


```{r}
properties1<-read.csv("/Users/4victoria98/Downloads/Labor Econ/Housing 1.csv")
properties2<-read.csv("/Users/4victoria98/Downloads/Labor Econ/Housing 2.csv")

head(properties1)
head(properties2)

houses_merge <- merge(properties1,properties2,by="PARID")
#head(houses_merge)

wilkinsburg<-houses_merge%>%filter(PROPERTYZIP.x==15221)
homewood<-houses_merge%>%filter(PROPERTYZIP.x==15208)
```

```{r}
homewood.and.wilkinsburg<-houses_merge%>%filter(PROPERTYZIP.x==15208 | PROPERTYZIP.x==15221)

```

```{r}
homewood.and.wilkinsburg$wilkinsburg<-ifelse(homewood.and.wilkinsburg$MUNIDESC.y=="Wilkinsburg", 1,0)
```

```{r}
home_wilk<-homewood.and.wilkinsburg%>%filter(PRICE > 100000)
home_wilk$log.price<-log(home_wilk$PRICE)
home_wilk$bathrooms<-home_wilk$FULLBATHS + .5*home_wilk$HALFBATHS
home_wilk$year_sale<-year(dmy(home_wilk$RECORDDATE.x))-2000

home_wilk<-home_wilk%>%filter(year_sale>=0)

housing.reg<-lm(log.price~STORIES+bathrooms+ BEDROOMS+TOTALROOMS+CONDITION+YEARBLT + year_sale+LOTAREA + wilkinsburg + SCHOOLCODE.x + BSMTGARAGE + FINISHEDLIVINGAREA, home_wilk)

summary(housing.reg)
```


```{r}
fig1<-streetspecific%>%select(c("log.price", "bathrooms",  "BEDROOMS","TOTALROOMS", "CONDITION",  "year_sale", "LOTAREA",  "wilkinsburg", "FINISHEDLIVINGAREA" ))
fig1<-fig1[c(2:6, 180:185),]

write_csv(fig1,"/Users/4victoria98/Downloads/fig1.csv")

```


```{r}
streetspecific<-home_wilk%>%filter(PROPERTYADDRESS%in%c("PEEBLES ST","MIFFLIN AVE", "GREEN ST", "PANSY WAY","CHESTNUT ST", "EAST END AVE","S TRENTON AVE", "REBECCA AVE", "FRANKLIN AVE", "WAVERLY ST","BRASHEAR ST", "SOUTH AVE", "GUTHRIE ST"))
streetspecific

street.reg<-lm(log.price~STORIES+bathrooms+TOTALROOMS+CONDITION+YEARBLT + year_sale+LOTAREA + wilkinsburg  + FINISHEDLIVINGAREA , streetspecific)

summary(street.reg)
```
```{r}
streetspecific<-home_wilk%>%filter(PROPERTYADDRESS%in%c("ROSEDALE ST"))
streetspecific
```



```{r}
streetspecific<-home_wilk%>%filter(PROPERTYADDRESS%in%c("WOOD ST", "S TRENTON AVE","EAST END AVE","MAPLEWOOD AVE", "SINGER PL", "PITT ST", "ROSEDALE ST", "S BRADDOCK AVE", "MIFFLIN AVE","EDGERTON AVE","SAVANNAH AVE","CELERON ST","UNION ST","SUSQUEHANNA ST","BIDDLE AVE","WEST ST"))
streetspecific$area_sq<-streetspecific$LOTAREA**2

street.reg<-lm(log.price~bathrooms+ BEDROOMS+TOTALROOMS+CONDITION + year_sale+LOTAREA + area_sq+ wilkinsburg  + FINISHEDLIVINGAREA  + BSMTGARAGE, streetspecific)

summary(street.reg)
```
```{r}
wilk_millage<-14+29.5
pitt_millage<-8.06+10.25

wilk_millage/pitt_millage
```


```{r}
streetspecific$PROPERTYADDRESS<-as.factor(streetspecific$PROPERTYADDRESS)
streetspecific$pred_sale<-exp(predict(street.reg, streetspecific))
streetspecific$wilkinsburg<-0

flop_county<-streetspecific
flop_county$wilkinsburg<-1

streetspecific$cf_pred_sale<-exp(predict(street.reg,flop_county))
streetspecific
MUNIDESC.y
```

```{r}
vectP<-prices.df$`Pitt. Property Tax`
VectW<-prices.df$`Wilk. Property Tax`

taxP<-rep(0,195)
taxW<-rep(0,195)

for(i in 1:10){
  taxP<-taxP + vectP*(1/(1+0.02)**i)
  taxW<-taxW + VectW*(1/(1+0.02)**i)
}

prices.df$pitt.tax.infl<-taxP
prices.df$wilk.tax.infl<-taxW
prices.df$tax.dif.infl<-prices.df$wilk.tax.infl-prices.df$pitt.tax.infl

colnames(prices.df)<-c("City","Price", "Pitt. Price", "Wilk. Price", "Price Difference", "Pitt. Property Tax", "Wilk. Property Tax", "Tax Difference", "10 Year Tax Dif", "Pitt 10Yr Prop.Tax W/Inf.","Wilk 10Yr Prop.Tax W/Inf.", "10 Yr Tax Dif W/Inf" )

prices.df<-prices.df[,-c(1,2,8)]
prices.df
```

```{r}
mean(prices.df$`Price Difference`-prices.df$tax.dif.infl) 
mean(prices.df$`Price Difference`-prices.df$`10 Year Fees`) 

```


```{r}
prices.df<-streetspecific[,c(100,103,115,116)]%>%filter(!is.na(pred_sale)&pred_sale!=cf_pred_sale)
prices.df$price_dif<-prices.df$pred_sale-prices.df$cf_pred_sale
prices.df$pitt.tax<-prices.df$pred_sale*pitt_millage/1000
prices.df$wilk.tax<-prices.df$pred_sale*wilk_millage/1000
prices.df$tax.dif<-prices.df$wilk.tax-prices.df$pitt.ta
prices.df$tax.dif.10yrs<-prices.df$tax.dif*10

colnames(prices.df)<-c("City","Price", "Pitt. Price", "Wilk. Price", "Price Difference", "Pitt. Property1 Tax", "Wilk. Property Tax", "Tax Difference", "10 Year Fees")
mean(prices.df$`Price Difference`-prices.df$`10 Year Fees`) 
mean(prices.df$`10 Year Fees`)

prices.df
```

```{r}
library(lemon)
knit_print.data.frame <- lemon_print
```


```{r, render=lemon_print}
write_csv(prices.df,"/Users/4victoria98/Downloads/prices_df.csv")
```

```{r}
prices.df$`10 Year Fees`<-prices.df$`10 Year Fees`-1000
ggplot(prices.df, aes(x=`10 Year Fees`, y = `Price Difference`)) + geom_point() + theme_bw()+theme(axis.title.x=element_text(size=15), axis.title.y=element_text(size=16))
```
assessment in 2012 assessment, #assessment ratio rate of 1/2, 
the millage rate
local total

Ideas for paper: Millage rate * local total, adjusted to 2023 dollars?
